Module 9 Notes

5-number summary
  min
  1st quartile
  median
  3rd quartile
  max
  sometimes mean

Pulling from local computer
```{r}
install.packages("sjmisc")
library(tidyverse)

d<-read.csv("Country-Data-2016.csv")
names(d)
```

Pulling from github
```{r}
f <- "https://raw.githubusercontent.com/difiore/ada-2024-datasets/main/Country-Data-2016.csv"
d <- read_csv(f, col_names = TRUE)
names(d)
```

```{r}
summary(d)
unique(d$country)
#Can also do...
c<-length(unique(d$country))
print(c)
ncol(d)
```
Variables = 16
Observations = 248
How many countries = 248

```{r}
median(d$area, na.rm = TRUE)
median(d$population, na.rm = TRUE)

```

Create new density column
```{r}
d$density<-(d$population / d$area)

ncol(d)
```
Variables = 17 because of addition of density column.

Order countries by decreasing density 
```{r}
d <- d[order(-d$density), ]
```

Create new dataframe with top 20 highest densities and calculate median area. 
```{r}
s <- d[1:20, ]
med_area <- median(s$area, na.rm = TRUE)
med_area
```
Top 10 and bottom 10 density
```{r}
topten<-d[1:10, ]

bottomten<-d[order(d$density), ]
bottomten<-bottomten[1:10, ]

#OR

topten<-head(d,10)
bottomten<-tail(d,10)

#using tail function includes the countries with NA densities. Reordering by increasing density then extracting first 10 rows does NOT include NA densities. 
```


